\section{Empirical Evaluations}
\label{sec:evaluation}

We evaluate DeXposure-FM on the DeXposure dataset, focusing on two tasks: (i) \textit{multi-step forecasting} of edge-level exposures and network-level statistics, and (ii) \textit{financial stability analysis} including model-based forward-looking risk assessment and stress testing during major events (Terra/Luna, FTX).

\subsection{Dataset and Experimental Setup}
\label{subsec:dataset}

\paragraph{Data source.}
We use the DeXposure dataset constructed from DeFiLlama API data, spanning March 2020 to August 2025 (283 weekly snapshots). Each snapshot contains protocol nodes with TVL measurements and directed edges representing credit exposures between protocols.

\paragraph{Data statistics.}
Table~\ref{tab:data-stats} summarizes the dataset characteristics. The network exhibits high edge persistence (mean overlap ratio 98.5\%), reflecting the stable nature of DeFi protocol interconnections.

\begin{table}[t]
\centering
\small
\begin{tabular}{lr}
\hline
\textbf{Statistic} & \textbf{Value} \\
\hline
Total snapshots & 283 weeks \\
Time range & 2020-03-23 $\sim$ 2025-08-18 \\
Mean nodes per week & 5,676 \\
Mean edges per week & 30,424 \\
Mean edge overlap ratio & 98.5\% \\
Protocol categories & $\sim$15 classes \\
\hline
\end{tabular}
\caption{DeXposure dataset statistics.}
\label{tab:data-stats}
\end{table}

\paragraph{Temporal split.}
We use a two-stage evaluation protocol:

\textit{Stage 1: Model selection via walk-forward cross-validation.}
We apply expanding window walk-forward cross-validation on pre-2025 data with 15 folds. Each fold uses a minimum of 104 training weeks, 24 validation weeks (for early stopping), and 8 test weeks. The validation window is sized to ensure sufficient samples even at longer horizons: for $h=12$, we require $\geq 12$ validation weeks to construct valid forecast pairs. The window advances by 8 weeks per fold, accumulating more training data. This stage is used for hyperparameter selection and model comparison.

\textit{Stage 2: Hold-out evaluation.}
Final performance is reported on a strict 2025 hold-out set, which is never seen during training or validation:
\begin{itemize}
  \item \textbf{Training:} 2020-03-23 $\sim$ 2024-07-15 (225 weeks)
  \item \textbf{Validation:} 2024-07-22 $\sim$ 2024-12-30 (24 weeks, for early stopping)
  \item \textbf{Test:} 2025-01-06 $\sim$ 2025-08-18 (33 weeks, strict hold-out)
\end{itemize}
Stage 1 is used for hyperparameter tuning; all results reported in this paper are from Stage 2 hold-out evaluation.

\paragraph{Forecast horizons vs. CV windows.}
The 8-week CV window controls how the temporal folds slide; within each window, the model predicts at multiple forecast horizons $h \in \{1, 4, 8, 12\}$ weeks ahead. These are orthogonal: the CV window determines sample collection, while $h$ determines how far into the future each prediction extends.

\paragraph{Models compared.}
We compare three approaches:
\begin{enumerate}
  \item \textbf{GraphPFN:} Pre-trained GraphPFN encoder with frozen weights; only task-specific prediction heads are trained (linear probe).
  \item \textbf{DeXposure-FM:} Pre-trained GraphPFN encoder with end-to-end fine-tuning using differential learning rates.
\item \textbf{ROLAND:} Representative temporal GNN baseline with a 2-layer GCN encoder (hidden\_dim=64, out\_dim=32) and GRU temporal updates for recurrent state propagation, trained from scratch. Uses the same optimizer (Adam), learning rate ($5 \times 10^{-4}$), and training schedule as DeXposure-FM.
\end{enumerate}

\subsection{Task I: Multi-step Forecasting}
\label{subsec:forecast}

\paragraph{Targets.}
We evaluate forecasts at horizons $h \in \{1, 4, 8, 12\}$ weeks for:
\begin{enumerate}
  \item \textbf{Edge existence:} Binary prediction of whether edge $(p,q)$ exists at $t+h$.
  \item \textbf{Edge weight:} Regression on log-scaled edge weight for existing edges.
  \item \textbf{Node TVL change:} Regression on $\Delta_{p,t+h} = \log(1+\text{TVL}_{t+h}) - \log(1+\text{TVL}_t)$.
\end{enumerate}

\paragraph{Metrics.}
For edge existence, we report AUPRC (area under precision-recall curve) and AUROC. For edge weight and node predictions, we report MAE and RMSE on log-scaled values.

\paragraph{Results.}
Table~\ref{tab:main-results} presents the main forecasting results on the 2025 hold-out test set.
%% [Updated to h={1,4,8,12} with complete DeXposure-FM results from GPU server experiments]

\begin{table}[t]
\centering
\small
\setlength{\tabcolsep}{4pt}
\begin{tabular}{llcccccc}
\hline
& & \multicolumn{2}{c}{\textbf{Edge Exist}} & \multicolumn{2}{c}{\textbf{Edge Weight}} & \multicolumn{2}{c}{\textbf{Node $\Delta$TVL}} \\
\textbf{Model} & $h$ & AUROC & AUPRC & MAE & RMSE & MAE & RMSE \\
\hline
\multirow{4}{*}{DeXposure-FM}
& 1 & \textbf{0.995} & \textbf{0.972} & \textbf{2.465} & \textbf{3.388} & \textbf{0.056} & \textbf{0.400} \\
& 4 & \textbf{0.995} & \textbf{0.973} & \textbf{2.489} & \textbf{3.424} & \textbf{0.140} & \textbf{0.680} \\
& 8 & \textbf{0.994} & \textbf{0.967} & \textbf{2.554} & \textbf{3.509} & \textbf{0.229} & \textbf{0.890} \\
& 12 & \textbf{0.993} & \textbf{0.967} & \textbf{2.648} & \textbf{3.606} & \textbf{0.286} & \textbf{1.046} \\
\hline
\multirow{4}{*}{GraphPFN}
& 1 & 0.988 & 0.938 & 3.260 & 4.383 & 0.059 & 0.401 \\
& 4 & 0.988 & 0.940 & 3.189 & 4.049 & 0.142 & 0.682 \\
& 8 & 0.987 & 0.938 & 3.169 & 4.064 & 0.215 & 0.896 \\
& 12 & 0.986 & 0.936 & 3.136 & 4.130 & 0.324 & 1.056 \\
\hline
\multirow{4}{*}{ROLAND}
& 1 & 0.961 & 0.865 & 3.240 & 4.264 & 0.060 & 0.403 \\
& 4 & 0.962 & 0.868 & 3.242 & 4.162 & 0.141 & 0.684 \\
& 8 & 0.961 & 0.867 & 3.213 & 4.180 & 0.221 & 0.895 \\
& 12 & 0.961 & 0.866 & 3.195 & 4.177 & 0.279 & 1.058 \\
\hline
\multirow{4}{*}{Persistence}
& 1 & 0.763 & 0.604 & 2.487 & 4.296 & 0.057 & 0.403 \\
& 4 & 0.782 & 0.635 & 2.372 & 4.138 & 0.138 & 0.685 \\
& 8 & 0.749 & 0.580 & 2.618 & 4.400 & 0.213 & 0.899 \\
& 12 & 0.762 & 0.603 & 2.541 & 4.304 & 0.272 & 1.065 \\
\hline
\end{tabular}
\caption{Multi-step forecasting results on 2025 hold-out test set at horizons $h \in \{1,4,8,12\}$ weeks. DeXposure-FM = Finetuned Foundation Model, GraphPFN = Graph Prior Fitted Network with Frozen weights. \textit{Persistence} = naive baseline predicting $\hat{A}_{t+h} = A_t$, $\hat{W}_{t+h} = W_t$.}
\label{tab:main-results}
\end{table}

\paragraph{Key findings.}
\begin{enumerate}
  \item \textbf{Edge existence substantially exceeds persistence:} All models dramatically outperform the naive persistence baseline (AUPRC 0.58--0.64) that simply predicts ``last week's graph.'' DeXposure-FM achieves AUPRC 0.967--0.973, representing a 52--67\% relative improvement over persistence. This confirms the models learn meaningful temporal dynamics beyond network inertia.
  \item \textbf{Edge weight matches persistence:} Surprisingly, edge weight prediction shows no improvement over the persistence baseline (MAE 2.37--2.62). DeXposure-FM achieves MAE 2.465--2.648, comparable to or slightly worse than persistence at some horizons. This indicates that learned models excel at predicting \textit{which} edges exist, but predicting \textit{how much} exposure flows through them remains fundamentally challenging---the best strategy is often ``predict last week's value.''
  \item \textbf{Model value is in link prediction:} The primary value of DeXposure-FM lies in edge existence prediction. Compared to learned baselines, it achieves 3--8\% AUPRC improvement over GraphPFN and 10--12\% over ROLAND, while maintaining comparable weight and node predictions.
  \item \textbf{Node prediction degrades with horizon:} Node TVL change prediction degrades as expected: DeXposure-FM MAE increases from 0.056 ($h=1$) to 0.286 ($h=12$), matching persistence (0.057--0.272) at all horizons.
\end{enumerate}

\subsection{Task II: Financial Stability Analysis}
\label{subsec:stability}

We conduct comprehensive financial stability analysis, combining systemic risk measurement, historical shock analysis, and contagion simulation. This task directly addresses macro-prudential policy applications.

\paragraph{Model-based evaluation protocol (pseudo out-of-sample).}
For Task II components that rely on forecasts, we use a fixed DeXposure-FM forecaster trained on the pre-2025 training period and early-stopped on the pre-2025 validation period (Stage 2 in Section~\ref{subsec:dataset}). We then evaluate on the strict 2025 hold-out set without any model re-estimation or parameter updates during the test period. Each test week provides a prediction origin $t$, yielding multiple out-of-sample pairs $(t,t+h)$ for statistical evaluation. We compute risk metrics and stress-test outcomes on the predicted future network $\hat{G}_{t+h}$ and compare them to the realized network $G_{t+h}$. To handle protocol entry/exit, all network-level comparisons are computed on the common node set $V_t \cap V_{t+h}$.

\subsubsection{Systemic Risk Measurement}
\label{subsubsec:systemic-risk}

We compute protocol-level and network-level risk indicators for each weekly snapshot.

\paragraph{Protocol-level systemic importance score (SIS).}
For each protocol $p$, we define:
\begin{equation}
\text{SIS}_p = \alpha \cdot \text{PageRank}_p + \beta \cdot \text{TailExposure}_p + \gamma \cdot \log(\text{TVL}_p),
\label{eq:sis}
\end{equation}
where $\text{TailExposure}_p$ measures the concentration of $p$'s largest exposures (ratio of top-5 exposures to total), and $\alpha, \beta, \gamma$ are normalized weights summing to 1. We use equal weights $\alpha = \beta = \gamma = 1/3$ in the baseline specification; robustness to alternative weightings is discussed in Section~\ref{subsec:discussion}.

\paragraph{Sector spillover index.}
We aggregate exposures into a sector-to-sector matrix $\mathbf{S} \in \mathbb{R}^{K \times K}$, where $S_{ij}$ is the total exposure from sector $i$ to sector $j$. The spillover index is the HHI of off-diagonal elements:
\begin{equation}
\text{SpilloverIndex} = \text{HHI}\left(\{S_{ij} : i \neq j\}\right).
\end{equation}

\paragraph{Early-warning indicators.}
We track structural change rates that may signal emerging instability:
\begin{itemize}
  \item Density change: $\Delta\rho_t = (\rho_t - \rho_{t-1})/\rho_{t-1}$
  \item Concentration spike: $\Delta\text{HHI}_t > 2\sigma$ (two standard deviations above mean)
  \item Assortativity shift: rapid changes in degree correlation
\end{itemize}

\subsubsection{Model-based Forward-looking Risk Assessment}
\label{subsubsec:forward-looking-risk}

Beyond descriptive monitoring on observed networks, we use DeXposure-FM to enable forward-looking stability assessment by forecasting future exposure graphs and then computing stability measures on the predicted graphs.

\paragraph{Forward-looking risk metric prediction.}
For each horizon $h \in \{1,4,8,12\}$ and each test origin week $t$ in the 2025 hold-out, we forecast the exposure network $\hat{G}_{t+h}$ and compute risk metrics (e.g., TVL concentration, edge concentration, density, spillover index, and summary statistics of SIS). We then compare these predicted metrics to their realized counterparts computed on $G_{t+h}$, reporting accuracy via MAE/RMSE and correlation across test pairs.

\paragraph{Predictive stress testing via contagion simulation.}
We run the contagion simulation (Section~\ref{subsubsec:contagion}) on three networks for each test origin: the observed network at $t$, the predicted network $\hat{G}_{t+h}$, and the realized future network $G_{t+h}$. The key question is whether stress-test losses computed on $\hat{G}_{t+h}$ approximate those on $G_{t+h}$, enabling forward-looking macroprudential scenario analysis.

\subsubsection{Shock Event Analysis}
\label{subsubsec:shock-events}

We analyze model behavior during two major DeFi stress events.

\paragraph{Events analyzed.}
\begin{enumerate}
  \item \textbf{Terra/Luna collapse} (May 9, 2022): The UST algorithmic stablecoin lost its dollar peg, triggering cascading liquidations. Analysis window: April 25 -- May 23, 2022.
  \item \textbf{FTX collapse} (November 7, 2022): The FTX exchange failure and resulting contagion through FTT token exposures. Analysis window: October 31 -- November 21, 2022.
\end{enumerate}

\paragraph{Analysis framework.}
For each event, we examine a pre/event/post window. To avoid event leakage in the case study, we train an event-specific forecaster using only snapshots strictly prior to the event window, and then generate one-step-ahead forecasts within the event window. We report structural shifts and forward-looking stability measures:
\begin{enumerate}
  \item \textbf{Network structure changes:} TVL, edge count, Gini coefficient, HHI.
  \item \textbf{Forward-looking risk metrics:} predicted vs.\ realized stability indicators during the event window.
  \item \textbf{Predictive stress losses:} predicted vs.\ realized contagion losses under the same shock definitions.
\end{enumerate}

\paragraph{Results.}
Table~\ref{tab:shock-results} shows network structure changes during the two stress events.

\begin{table}[t]
\centering
\small
\begin{tabular}{lcccc}
\hline
\textbf{Event} & \textbf{Pre-TVL (\$B)} & \textbf{Post-TVL (\$B)} & \textbf{$\Delta$TVL} & \textbf{$\Delta$Edges} \\
\hline
Terra/Luna & 257.1 & 171.0 & $-$33.5\% & +9.4\% \\
FTX & 127.0 & 177.2 & +39.5\% & $-$3.3\% \\
\hline
\end{tabular}
\caption{Network structure changes during stress events. Terra/Luna shows a classic flight-to-quality pattern with TVL collapse but edge count increase as capital reorganizes across protocols. The FTX event shows a \emph{positive} $\Delta$TVL because our dataset captures only on-chain DeFi protocols: the collapse of a centralised exchange triggered capital migration \emph{into} DeFi as users withdrew funds to self-custody, consistent with the ``flight to decentralisation'' narrative \citep{VidalTomasEtAl2023FTX}.}
\label{tab:shock-results}
\end{table}

\subsubsection{Contagion Simulation}
\label{subsubsec:contagion}

We implement a DebtRank-style contagion simulation to assess systemic loss propagation.

\paragraph{Shock propagation mechanism.}
Given an initial shock to protocol $p_0$ with loss ratio $\delta_0$:
\begin{enumerate}
  \item \textbf{Initialize:} $\text{Loss}_{p_0} = \delta_0 \cdot \text{TVL}_{p_0}$
  \item \textbf{Propagate:} When a distressed debtor $p$ has loss $\text{Loss}_p$, we allocate its loss to its creditors $q$ proportionally to their exposures $E_{qp}$:
  \begin{equation}
    \Delta \text{Loss}_q \;=\; \text{Loss}_p \cdot \frac{E_{qp}}{\sum_{q'} E_{q'p}}.
  \end{equation}
  \item \textbf{Iterate:} If $\text{Loss}_q > \tau \cdot \text{TVL}_q$ (with distress threshold $\tau = 0.1$, i.e., 10\% TVL loss), protocol $q$ becomes distressed and then propagates losses to its creditors. Losses are capped at $\text{TVL}_q$.
  \item \textbf{Terminate:} When no new protocols become distressed.
\end{enumerate}

\paragraph{Simulation scenarios.}
We simulate counterfactual shocks using actual network structure:
\begin{itemize}
  \item \textbf{Stablecoin de-peg:} 50\% TVL loss to major stablecoins (USDC, DAI)
  \item \textbf{Exchange failure:} Complete TVL loss to centralized exchange protocols
  \item \textbf{Bridge exploit:} 100\% loss to cross-chain bridge protocols
\end{itemize}

\paragraph{Metrics.}
\begin{itemize}
  \item \textbf{Total system loss:} $\sum_p \text{Loss}_p$ after convergence
  \item \textbf{Contagion depth:} Number of propagation rounds before convergence
  \item \textbf{Affected protocols:} Count of protocols with $\text{Loss} > 0$
\end{itemize}

Table~\ref{tab:contagion-results} presents contagion simulation results on the May 2022 network snapshot (4,329 nodes, 17,721 edges).

\begin{table}[t]
\centering
\small
\begin{tabular}{lccc}
\hline
\textbf{Scenario} & \textbf{System Loss (\%)} & \textbf{Depth} & \textbf{Affected} \\
\hline
Single protocol (50\% shock) & 0.00 & 0 & 0 \\
Multi-protocol (top 5) & 0.00 & 0 & 0 \\
Stablecoin cluster & 1.10 & 1 & 153 \\
Bridge exploit (100\% loss) & \textbf{5.27} & 1 & 90 \\
\hline
\end{tabular}
\caption{Contagion simulation results. Bridge protocols emerge as the primary systemic risk vector---despite shocking only 22 nodes, they cause the largest system-wide loss (5.27\% TVL). Single-protocol failures show minimal contagion, indicating network resilience to isolated shocks.}
\label{tab:contagion-results}
\end{table}

\subsection{Discussion}
\label{subsec:discussion}

\paragraph{Edge existence is the key prediction task.}
The 98.5\% mean edge overlap in DeFi networks means that a naive persistence baseline (``predict last week's graph'') achieves only AUPRC 0.58--0.64 for edge existence---substantially below learned models. DeXposure-FM's 52--67\% relative AUPRC improvement over persistence (0.967--0.973 vs.\ 0.58--0.64) demonstrates that the model learns meaningful structural dynamics beyond network inertia. This is the primary source of model value.

\paragraph{Weight prediction remains fundamentally hard.}
Contrary to expectations, edge weight prediction shows no improvement over the naive persistence baseline. DeXposure-FM achieves MAE 2.465--2.648, comparable to persistence (2.37--2.62). This suggests that exposure magnitudes are inherently difficult to forecast: the best predictor of next week's exposure is often this week's exposure. While DeXposure-FM improves substantially over other \textit{learned} baselines (GraphPFN: 3.14--3.26, ROLAND: 3.20--3.24), the persistence baseline reveals that these learned models were inefficiently encoding temporal structure that could be captured by a simple heuristic. The practical implication is that model value lies in predicting \textit{which} edges exist, not \textit{how much} flows through them.

\paragraph{Bridge protocols as systemic risk vectors.}
Contagion simulations identify cross-chain bridges as disproportionate risk concentrators---shocking 22 bridge nodes causes 5.27\% system-wide loss, exceeding stablecoin scenarios (79 nodes, 1.10\% loss). This aligns with historical bridge exploits (Ronin, Wormhole) and suggests regulatory attention to bridge capitalization.

\paragraph{Limitations.}
The contagion model assumes linear loss propagation and does not capture feedback effects (e.g., liquidation cascades). Node TVL predictions degrade at longer horizons (MAE 0.056 at $h=1$ vs.\ 0.286 at $h=12$), reflecting inherent uncertainty in protocol-level forecasts beyond 2--3 months.
