\IEEEraisesectionheading{\section{Introduction}\label{sec:introduction}}

In May 2022, the Terra/Luna collapse erased over \$40 billion in value within 48~hours, triggering cascading liquidations across lending protocols, DEXs, and yield aggregators that held UST-denominated assets. Five months later, the FTX insolvency exposed hidden cross-protocol exposures and wiped out another \$8 billion. These crises share a common pattern: shocks propagated through an interconnected web of tokenised liabilities---credit exposures---that no single participant fully observed. In decentralised finance, exposures are high-dimensional, time-varying, and often implicit; data are noisy and incomplete; and crises unfold within days, leaving limited time for manual assessment.

Automated \emph{agentic} pipelines offer a principled response: an agent can ingest on-chain measurements, maintain a belief over the evolving exposure network, surface early-warning signals, stress-test plausible shocks, and recommend risk-mitigating actions with auditable rationale. However, existing agentic proposals for DeFi risk largely rely on general-purpose large language models or static heuristics, and lack a dedicated forecasting backbone for graph-structured time series. Without accurate and data-efficient prediction of network dynamics, monitoring agents suffer from high false-alarm rates and delayed detection, while decision agents risk recommending actions based on brittle or poorly calibrated beliefs. In high-stakes contexts, uncertainty calibration and robustness to missingness and regime shifts are not optional---they determine whether an agent is trusted and deployable.

This paper addresses that bottleneck by building an agentic system around a strong graph time-series foundation model, and---in tandem---by providing the evaluation suite the community needs to compare such systems. We leverage \textsc{DeXposure-FM}, a foundation model trained on over $43.7$~million data entries from DeFi exposure networks, designed to forecast the evolution of credit-exposure graphs across multiple horizons. On top of this backbone we present \textsc{DeXposure-Claw}, a modular four-layer query architecture that follows a \emph{forecast--measure--decide} paradigm, and \textsc{DeXposure-Bench}, a standardised evaluation suite that benchmarks FM+LLM decision pipelines on a shared regulator-aligned ground truth.

Our contributions are:
\begin{enumerate}[leftmargin=*, itemsep=2pt]
    \item \textbf{\textsc{DeXposure-Claw}: a four-layer agentic architecture for DeFi exposure-network risk} (\S\ref{sec:algorithm}). We design and implement an end-to-end system organised as four layers---FM prediction, deterministic monitor and scenario engines, LLM decision, and a safety gate---that transforms forecasted exposure graphs into auditable supervisory tickets. The monitor, scenario, and safety-gate layers are deterministic and reproducible; the LLM decision layer is governed by per-ticket audit logs and exhibits $0.78$--$0.86$ inter-run Jaccard consistency. Five network risk metrics with rolling baselines, five standardised stress scenarios with CVaR aggregation, and a four-level playbook gated by data-health and confidence checks complete the design. While prior agentic work in DeFi targets transaction verification~\cite{yao2025arbiter} or intent mining~\cite{mao2025knowyourintent}, and graph-based foundation models for risk have been explored only in traditional finance~\cite{li2025hgmae}, no existing system unifies these capabilities for DeFi exposure networks.

    \item \textbf{Empirical effectiveness of the FM\,+\,LLM agentic stack with quantified Pareto trade-offs} (\S\ref{sec:exp}). On \textsc{DeXposure-Bench} we show that \textsc{DeXposure-Claw} (FM\,+\,LLM\,+\,gate) raises end-to-end ticket F1 from $0.0076$ (persistence\,+\,rules) to $0.0233$ (\textbf{$+208\%$}) and LLM-as-judge explanation quality from $2.03$ to $2.69/5$ (\textbf{$+33\%$}). The forecasting layer is useful for monitoring rather than uniformly better on every point metric: TrendCons@h4 reaches $0.628$ against EvolveGCN's $0.324$ and a structurally pinned $0$ for persistence, prediction intervals are calibrated (coverage $0.913$ vs $0.90$ target, ECE $0.013$), and median early-warning lead time is $4$--$5$ weeks across Terra/Luna, FTX, and SVB-USDC. Layer-wise attribution against two distinct baselines makes the gains decomposable: adding the FM signal to a snapshot LLM (\texttt{m2\_snapshot\_llm}$\to$\texttt{m6\_fm\_llm}) lifts F1 by $+32\%$; replacing rules with an LLM under a fixed FM predictor (\texttt{m5\_fm\_rules}$\to$\texttt{m6\_fm\_llm}) lifts F1 by another $+27\%$. The bench also exposes the cost: FM\,+\,LLM variants raise recall and explanation at a non-trivial false-intervention rate ($\mathrm{FIR}\approx 0.44$ vs $0$ for rule-based baselines), while the safety gate trades $3\%$ F1 for $+0.21$ judge score and $+10\%$ run-to-run consistency.

    \item \textbf{\textsc{DeXposure-Bench}: a reusable testbed for FM\,+\,LLM decision pipelines on temporal exposure graphs} (\S\ref{sec:bench}). We release a standardised harness that scores a candidate pipeline on six axes---forecasting quality, streaming anomaly detection, predictive uncertainty, what-if scenario fidelity, supervisory decision quality, and data-quality robustness. The bench operates on the full \textsc{DeXposure} corpus ($4{,}300$ protocols, $24{,}300$ tokens, $43.7$M exposure entries, $283$ weekly snapshots from $2020$ to $2025$~\cite{wu2025dexposuredatasetbenchmarksinterprotocol}), uses a regulator-aligned ground truth defined by \emph{absolute} weight loss rather than fractional change, and ships eight reference method implementations covering persistence, EvolveGCN, snapshot-LLM, FM-only, FM\,+\,rules, and three FM\,+\,LLM configurations. Generic LLM-agent benchmarks (\textsc{SWE-bench}, \textsc{AgentBench}, \textsc{HELM}) do not evaluate domain-grounded decisions, and temporal-graph benchmarks (\textsc{TGB}, \textsc{OGB}) stop at structural prediction; \textsc{DeXposure-Bench} fills this benchmark gap for agentic risk pipelines.
\end{enumerate}

We will release the implementation and benchmark artifacts with the project repository.
