\section{Limitations}
\label{sec:limitations}

We disclose three limitations that bound the scope of our claims.

\paragraph{Single dataset} All results are reported on the \textsc{DeXposure} weekly exposure-graph dataset. While it covers $4{,}300$ protocols, $24{,}300$ tokens, $43.7$M exposure entries, and $283$ weekly snapshots spanning the major DeFi crisis episodes of $2020$--$2025$, generalisation to other on-chain risk surfaces---NFT lending, perpetual derivatives, or cross-chain bridge networks---is untested and will require domain-specific re-calibration of the conformal split and the stressed-set percentile $\pi$.

\paragraph{Weekly temporal resolution} The forecast and decision pipeline operates at weekly granularity. Many DeFi shocks unfold within hours---the Terra/Luna collapse erased $\$40$B in under $48$ hours---and a production deployment would require sub-hourly snapshots and re-evaluation of conformal calibration on the resulting denser time series. The historical \texttt{b2\_warning} lead times of $4$--$5$ weeks should therefore be read as ``how early the weekly monitor turns'', not as end-to-end alert latency.

\paragraph{Offline decision evaluation} \texttt{b5\_decision} scores tickets against a regulator-aligned absolute-loss ground truth, and the explanation-quality metric is an LLM-as-judge proxy. The headline configuration uses Claude~Opus~4.7 as the decision LLM and Claude~Opus~4.8 as the within-family tier-above judge; a cross-family panel of Gemini~2.5~Pro and GPT-5.5 (Table~\ref{tab:judge_panel}) is reported as a robustness check, alongside Claude~Haiku~4.5 from the v1 pilot as a tier-below weak-judge baseline. None of these captures the downstream effect of supervisory action---whether the recommended risk reduction would actually have averted contagion. A controlled live evaluation with a regulator in the loop, which the bench approximates but cannot replace, remains the primary direction we plan to extend the benchmark in.

\paragraph{Judge thinking-budget is held minimal} The cross-family judges in Table~\ref{tab:judge_panel} (Gemini~2.5~Pro, GPT-5.5) are reasoning-by-default frontier models; we attach OpenRouter's $\mathrm{reasoning}\!=\!\{\mathrm{effort:minimal}\}$ control so the comparison against the non-reasoning Anthropic baseline is apples-to-apples on intrinsic capability rather than thinking budget. Default reasoning mode would change the reported scores; we treat the reasoning-on configuration as a distinct evaluation surface and leave it for a follow-up study. Practitioners deploying the judge at default reasoning settings should re-calibrate the score thresholds reported here. Human-judge calibration with practising supervisors remains the most pressing methodological extension.
