\section{Introduction}
\label{sec:intro}

In May 2022 the Terra/Luna collapse erased over \$40 billion in
48~hours, triggering cascading liquidations through lending protocols,
DEXs, and yield aggregators that held UST-denominated
assets~\citep{VidalTomasEtAl2023FTX}. Five months later FTX wiped out
another \$8 billion. These crises were not isolated: in
decentralised finance (DeFi), credit exposures form a dense,
time-varying network of tokenised claims that no single participant
fully observes, and shocks travel through it within hours.

A natural response is to build an \emph{agent}: an LLM-driven
pipeline that ingests on-chain measurements, surfaces early-warning
signals, and recommends risk-mitigating actions with auditable
rationale. Our reference implementations (\S\ref{sec:results}) show
that the obvious designs fail in two ways. Reading raw on-chain
snapshots, the LLM is conservative but weak: poorly targeted
tickets (F1 $0.0183$), and the lowest-scored rationales under every
judge we test. Fed richer \emph{forecasted} evidence, it targets
better but \emph{hallucinates severity}: every cited number is
traceable to the evidence bundle (grounding $1.000$), yet $44.8\%$
of its intervention-level tickets point at protocols that are never
actually stressed. In a supervisory setting the second failure is
far costlier than missed detections, because every intervention is
observable and politically expensive.

To measure such a failure mode honestly we first need a ground
truth that matches how supervisors actually prioritise. Prior
systemic-risk evaluations rank protocols by \emph{fractional} weight
change~\citep{BERTOMEU2024105321,gonon2025computingsystemicriskmeasures,
li2025hgmae}, which over-weights tiny protocols of low systemic
relevance and is not what a supervisor ranks by. \textbf{We define
a regulator-aligned \emph{absolute-loss} ground truth}
(\S\ref{sec:bench}) and use it to score, for the first time, an
integrated forecast$+$monitor$+$scenario$+$LLM$+$gate pipeline
against what a supervisor would actually prioritise. The
characterisation produces the first joint measurement of forecast
quality, monitor lead time, and ticket quality on the same
regulator-aligned target, and the first quantification of the
false-intervention cost for an LLM agent operating in this
setting---a cost that finance-specific LLM-agent
work~\citep{yao2025arbiter,mao2025knowyourintent,luo2025llmcrypto,
jeon2026blindtrade} has not measured, since none of those systems
is scored against a regulator-aligned ground truth.

We close this gap with three contributions:
\begin{itemize}[leftmargin=*,itemsep=2pt,topsep=2pt]
    \item \textbf{A deployment-ready LLM-agent supervisory pipeline}
    (\sysname; \S\ref{sec:pipeline}). A graph time-series
    foundation model (\fmname) produces predicted exposure networks;
    five deterministic monitors and five stress scenarios convert
    them into a typed evidence bundle; an LLM emits supervisory
    tickets with rationale; and two safety gates (data-health,
    confidence) determine when intervention-level tickets are
    allowed.

    \item \textbf{An evaluation harness}
    (\benchname; \S\ref{sec:bench}). Six axes spanning
    forecast quality, streaming anomaly detection, predictive
    uncertainty, what-if scenario fidelity, supervisory ticket
    quality, and data-quality robustness, with a regulator-aligned
    \emph{absolute-loss} ground truth (\S\ref{sec:bench}) and eight
    reference method implementations including persistence, EvolveGCN
    \citep{ParejaEtAl2020EvolveGCN}, rule engines, snapshot LLMs, and
    \fmname-coupled LLM variants.

    \item \textbf{An operating-point characterisation}
    (\S\ref{sec:results}). On the frozen 2025 split of
    \corpusname, the full \fmname$+$LLM$+$gate stack
    raises ticket F1 from $0.0076$ to $0.0233$ ($+207\%$). A
    tier-above Claude~Opus~4.8 judge
    \citep{Zheng2023LLMJudge} and a cross-family panel
    (Gemini~2.5~Pro, GPT-5.5) all rank the gated stack
    \texttt{m7} highest on explanation quality; under the
    Opus~4.7 decision LLM the false-intervention rate rises to
    $\approx 0.44$. A tier-below Sonnet~4.6 decision LLM yields a
    Pareto improvement on both \texttt{m6} and \texttt{m7}:
    F1 rises further to $0.0288$, FIR collapses to $0.000$, and
    judge quality reaches $2.65$, at $\sim$5$\times$ lower
    inference cost---the deployable headline operating point.
\end{itemize}

\noindent
\textbf{Honest scope and track fit.} We have run the pipeline as a
historical backtest over $283$ weekly snapshots of real
DefiLlama-sourced exposure data (2020--2025), not as a live
production cron at a supervisory authority. The contribution is
therefore best read as \emph{methods for deployed systems
(evaluation, ethics, robustness)} and \emph{insights based on
real-world datasets}---two of the Industry Track's explicit
categories---rather than as a deployment case study.
The released ticket-level audit logs come from the backtest,
letting operators recompute the operating point under their own
data conditions before adopting the system.
