\section{Related Work}
\label{sec:related}

\paragraph{Bench positioning and ground-truth definition.}
LLM-agent benchmarks (HELM~\citep{liang2022helm},
SWE-bench~\citep{jimenez2024swebench},
AgentBench~\citep{liu2024agentbench}) score open-ended reasoning,
software repair, and generic agent behaviour; temporal-graph
benchmarks (TGB~\citep{huang2023tgb}, OGB~\citep{hu2020ogb}) score
structural prediction quality. Neither scores whether an LLM agent's
supervisory decisions match what a regulator would actually
prioritise. The closest prior systemic-risk evaluations
\citep{BERTOMEU2024105321,gonon2025computingsystemicriskmeasures,
li2025hgmae} rank protocols by \emph{fractional} weight change, which
disproportionately surfaces tiny protocols of low systemic relevance.
\benchname{} replaces this with an \emph{absolute-loss} ground
truth (\S\ref{sec:preliminaries}).

\paragraph{LLM agents in finance and DeFi.}
General agent patterns such as ReAct~\citep{YaoEtAl2023ReAct}
combine reasoning with tool use; FinGPT~\citep{YangEtAl2023FinGPT}
adapts language models to financial data. Within DeFi, agentic
systems have so far targeted transaction
auditing~\citep{yao2025arbiter}, intent
mining~\citep{mao2025knowyourintent}, smart-contract
verification~\citep{hu2026heimdallr,kong2026knowdit}, price
manipulation~\citep{liu2025pmdetector}, and explanation for graph
anomalies~\citep{watson2025explainfirst}; portfolio-oriented agents
combine graph encoders with LLMs~\citep{luo2025llmcrypto,
jeon2026blindtrade}. These systems consume raw transactions or token
text, not structured forecasted evidence, and none reports a
false-intervention rate against a regulator-aligned ground truth---a
gap our characterisation (\S\ref{sec:results}) closes.

\paragraph{Forecast-grounded LLM agents in other domains.}
Pairing a domain forecaster with an LLM decision layer is an emerging
deployment pattern. In macroeconomics, ChatGPT-augmented PMI
nowcasting~\citep{deBondtSun2025ChatGPTNowcast} and LLM-driven
macroeconomic forecasting~\citep{CarrieroEtAl2024MacroLLM} both feed
structured numeric inputs into an LLM that produces interpretable
narratives; a BIS primer surveys the wider
pattern~\citep{KwonEtAl2024BISLLMprimer}. Time-series foundation
models such as Chronos~\citep{AnsariEtAl2024Chronos},
Lag-Llama~\citep{RasulEtAl2023LagLlama}, and
TimesFM~\citep{DasEtAl2024TimesFM} make the forecaster reusable
across tasks; tabular foundation models extend the same idea to
heterogeneous structured data~\citep{HollmannEtAl2025TabPFN,
eremeev2025turningtabularfoundationmodels}. None of these
forecast$\to$LLM pipelines, to our knowledge, has been scored
against a regulator-aligned ground truth for high-stakes
financial-network supervision.
