\section{Evaluation Harness}
\label{sec:bench}

\paragraph{Why a new harness.}
Scoring an LLM-agent supervisory pipeline requires evidence on six
independent axes that no existing benchmark covers together: how
good is the forecast (\texttt{b1\_forecast}), how early does the
monitor turn (\texttt{b2\_warning}), is the predictive uncertainty
calibrated (\texttt{b3\_calibration}), do scenario losses match
reality (\texttt{b4\_stress}), do the emitted tickets match what a
regulator would prioritise (\texttt{b5\_decision}), and what happens
under degraded data (\texttt{b6\_robustness}). No existing
benchmark covers these axes together (\S\ref{sec:related});
\benchname{} unifies them on a shared dataset and
reference-method set so layer-wise ablations can be reported
independently.

\paragraph{Dataset and split.}
We use the \corpusname{} dataset of weekly directed weighted
exposure graphs (4{,}300 protocols, 24{,}300 tokens, $43.7$M
exposure entries, $283$ weekly snapshots from 2020-03 to 2025-08
\citep{wu2025dexposuredatasetbenchmarksinterprotocol}). We adopt a
strict no-leakage temporal split: 2020-03--2024-06 train
($\sim$222~weeks), 2024-07--2024-12 validation ($\sim$26~weeks, used
for conformal calibration and threshold tuning), 2025-01--2025-08
test ($\sim$33~weeks, frozen leaderboard). All \fmname{}
fine-tuning and model selection likewise use pre-2025 data only
(\S\ref{app:fm-notation}). For
\texttt{b2\_warning} we additionally run a historical event study
around Terra/Luna (2022-05-09), FTX (2022-11-07), and SVB/USDC
(2023-03-10); the event study is reported separately from the 2025
predictor-specific leaderboard.

\paragraph{Regulator-aligned absolute-loss ground truth.}
Prior systemic-risk evaluations rank protocols by \emph{fractional}
weight change, which silently up-weights tiny protocols of low
systemic relevance. \benchname{} ranks instead by \emph{absolute}
loss, scoring tickets against the stressed set $\mathcal{S}_t^h$
and FIR of \S\ref{sec:preliminaries}.
We fix $\pi\!=\!0.05$ and the ground-truth horizon $h\!=\!4$~weeks
throughout (yielding $|\mathcal{S}_t^h|\!\approx\!283$ protocols
per week); the last four test weeks lack a $4$-week-ahead
snapshot, so decision axes score $n\!=\!29$ weeks. The same
ground truth anchors
\texttt{b2\_warning}, \texttt{b5\_decision}, and the LLM-decision
evaluation pipeline.

\paragraph{Eight reference implementations.}
The harness bundles eight reference methods spanning the four
ablation cuts of the four-layer framework: heuristic streaming
monitor (\texttt{h1}), persistence$+$rules (\texttt{m1}), snapshot
LLM (\texttt{m2}), EvolveGCN~\citep{ParejaEtAl2020EvolveGCN}
(\texttt{m3}), \fmname-only (\texttt{m4}),
\fmname$+$rules (\texttt{m5}), \fmname$+$LLM
(\texttt{m6}), and \fmname$+$LLM$+$gate (\texttt{m7}). Each
method exposes the same \texttt{predict\_graph} or
\texttt{decide\_actions} interface so adding a ninth method is a
single-file change. The full method specification and per-axis
schema are in \S\ref{app:bench-details}--\S\ref{app:reference-methods}.

\paragraph{Reproducibility.}
A complete leaderboard run finishes in under four GPU-hours on a
single RTX~4090 plus approximately \$10 of LLM API spend, making the
harness accessible without industrial compute. The harness fixes
seeds, snapshots library versions, and hashes checkpoints; every
reported number reproduces bit-exactly from the released
artefacts.
