\section{Experiments}
\label{sec:evaluation}
\label{sec:bench}

\paragraph{Metrics and ground truth.}
\benchname{} scores the pipeline on six axes that span forecasting,
warning, and decision quality: forecast quality
(\texttt{b1\_forecast}), warning lead time (\texttt{b2\_warning}),
uncertainty calibration (\texttt{b3\_calibration}), stress-scenario
losses (\texttt{b4\_stress}), regulator-prioritised tickets
(\texttt{b5\_decision}), and degraded-data robustness
(\texttt{b6\_robustness}). The decision and warning axes share the
absolute-loss ground truth of \S\ref{sec:preliminaries}, avoiding
fractional-change rankings that over-weight tiny protocols. We fix
$\pi\!=\!0.05$ and $h\!=\!4$ weeks, yielding
$|\mathcal{S}_t^h|\!\approx\!283$ protocols per week; decision axes
score $n\!=\!29$ test weeks because the final four snapshots lack a
4-week-ahead target.

\paragraph{Data, splits, and baselines.}
All experiments run on \corpusname{} weekly exposure graphs under a
strict temporal split, against eight bundled reference
implementations. The corpus holds 4{,}300 protocols,
24{,}300 tokens, $43.7$M exposure entries, and $283$ snapshots from
2020-03 to 2025-08 \citep{wu2025dexposuredatasetbenchmarksinterprotocol}.
All model selection uses pre-2025 data: 2020-03--2024-06 train and
2024-07--2024-12 validation; 2025-01--2025-08 is the frozen test
split. The harness bundles eight reference implementations:
\texttt{h1}, \texttt{m1}--\texttt{m7}, spanning heuristic monitors,
persistence, snapshot LLM, EvolveGCN~\citep{ParejaEtAl2020EvolveGCN},
\fmname{}, rules, LLM decisions, and safety gates. Full schemas and
method details are in \S\ref{app:bench-details}--\S\ref{app:reference-methods};
the historical Terra/Luna, FTX, and SVB/USDC warning study is
reported separately from the 2025 leaderboard.

\paragraph{Reproducibility.}
The full leaderboard is cheap to reproduce end to end. A complete
run finishes in under four GPU-hours on a
single RTX~4090 plus approximately \$10 of LLM API spend. The
harness fixes seeds, versions, and checkpoint hashes; every reported
number reproduces from the released artefacts.
