\section{Deployment Lessons}
\label{sec:lessons}

We surface four lessons from building \sysname{} that we expect to
transfer to other forecast$\to$LLM pipelines for high-stakes
structured-evidence decisions.

\paragraph{L1. Grounding $\ne$ correctness.}
Our LLM variants achieve grounding score $1.000$: every cited number
in every emitted ticket is traceable to a field of the input
evidence bundle. They still pay $\mathrm{FIR}\!=\!0.448$. The failure
is not that the LLM invents evidence; it is that the LLM
\emph{over-reads} weak-but-present evidence as a justification for
high-severity action. Grounding tells you the agent did not
hallucinate citations; only a downstream metric that measures
intervention realism (FIR against an absolute-loss ground truth) tells
you whether the agent is safe to act on.

\paragraph{L2. Audit logs are a design artefact, not an output.}
Every emitted ticket carries the forecast distribution, monitor
scores, scenario CVaRs, the LLM rationale, the gate states, and the
seeds that produced it. We release these ticket-level audit logs
because the operating point we report is not what every operator
will need: a more conservative supervisor will retune
$\tau_{\mathrm{data}}$ or $\tau_{\mathrm{conf}}$ and rerun the
decision policy without re-invoking the FM or the LLM. Audit logs
treated as a first-class artefact make the system retunable
post-hoc.

\paragraph{L3. Safety gates are reserves, not always-on filters.}
On clean 2025 data the data-health gate is dormant
(\S\ref{sec:results}); its impact is invisible to a leaderboard
that does not include a degradation track. Under masking regimes,
the gate suppresses up to $60\%$ of FIR-eligible tickets at the cost
of suspending intervention-level actions. The deployable lesson is
to evaluate gates on dedicated stress regimes rather than on clean
test splits; if you only evaluate on the latter you will conclude
the gate is unnecessary and ship without it.

% L4 (Cadence fits an academic budget) removed: the cost claim
% (~5x lower inference cost with Sonnet 4.6 + weekly cron on a
% single RTX 4090) is now covered by Table 3 caption + §5 narrative.

% Closing paragraph removed in v3: the backtest-not-deployment
% disclosure is already in Limitations and the intro's "Honest
% scope and track fit"; repeating it here pushed the Conclusion
% across the 6-page boundary.
