\section*{Ethics Statement}
\label{sec:ethics}

\paragraph{Data provenance.}
\corpusname{} is built from public on-chain measurements
aggregated via DefiLlama~\citep{DefiLlama2026}. No private user data,
wallet-level personally-identifying information, or off-chain
identity data is used. Protocol-level aggregates are the unit of
analysis throughout.

\paragraph{Decision risk.}
\sysname{} emits supervisory tickets, not automated trades or
automated interventions. The high-severity action types
(\texttt{Recommend-Reduce}, \texttt{Contingency}) are gated on a
data-health score and a confidence score, and the pipeline emits a
safe-mode notice when either gate fails. We characterise the system
as decision support for a human supervisor, not as an autonomous
risk agent. The measured false-intervention rate
($\mathrm{FIR}\!\approx\!0.44$ for the \fmname$+$LLM variant) is
reported in the headline results table so that downstream operators
can weigh the trade-off against their own risk tolerance before
deployment.

\paragraph{LLM use disclosure.}
The decision-layer LLM (\texttt{m2}, \texttt{m6}, \texttt{m7}) is
Claude Opus~4.7 in the main configuration; Claude Sonnet~4.6 and
Google Gemini~2.5~Pro are reported as decision-layer ablations.
The LLM-as-judge for the explanation-quality axis is a
three-model cross-family panel: Claude Opus~4.8 (within-family
upgrade, strictly tier-above Opus~4.7), Google Gemini~2.5~Pro,
and OpenAI GPT-5.5 (cross-family). All judges are run with
reasoning effort set to \emph{minimal} so the comparison is
controlled for thinking budget. Claude Haiku~4.5 from a prior
run is reported in the appendix as a weak-judge baseline. Every
model is accessed through the OpenRouter unified API at
temperature~$0$.

\paragraph{Release.}
We will release the harness, the eight reference implementations,
and the ticket-level audit logs under a permissive open licence.
Model checkpoints will be released subject to dataset-licence
compatibility checks.
