\section{Additional Algorithm Details}
\label{app:pipeline-math}

Section~\ref{sec:preliminaries} defines the exposure graph, forecast
distribution, predicted graph, monitor alert rule, scenario loss, ticket
metrics, and gate feasibility conditions used throughout the paper. This
appendix records only the concrete instantiation used by \sysname{}.

\subsection{Forecast instantiation}
\label{app:fm-notation}

At each decision epoch $t$, \sysname{} queries \fmname{} once for each
horizon $h\in\{1,4,8,12\}$ and constructs $\widehat{G}_{t+h}$ with the
expected-weight operator from Section~\ref{sec:preliminaries}. We set the
edge-existence threshold to $\pi_{\min}=0.2$, tuned on the validation split.
Uncertainty summaries use $M=50$ Monte Carlo graph samples. Each sample first
draws edge indicators from the predicted edge probabilities, then perturbs
positive edge weights with the forecaster's predictive regression spread. For
existing edges, residual predictions are folded into the conditional mean
$\mu_{pq,t+h}$ before applying the expected-weight construction; candidate
new edges enter only when their predicted existence probability exceeds
$\pi_{\min}$.

\subsection{Monitor instantiation}

\begin{center}\small
\begin{tabular}{@{}lll@{}}
\toprule
ID & Metric                & Definition \\
\midrule
N1 & Systemic Importance  & $\max_{p\in V}\mathrm{PageRank}(\widehat{G}_{t+h})_p$ \\
N2 & HHI Concentration    & $\sum_p (d_p / \sum_q d_q)^2$, $d_p=\sum_q\widehat{w}_{pq,t+h}$ \\
N3 & Network Density      & $|\widehat{E}_{t+h}| / |V|(|V|-1)$ \\
N4 & PageRank Gini        & $\mathrm{Gini}(\{\mathrm{PageRank}_p\}_{p\in V})$ \\
N5 & Degree Gini          & $\mathrm{Gini}(\{d_p\}_{p\in V})$ \\
\bottomrule
\end{tabular}
\end{center}

All monitors use the rolling alert rule from
Section~\ref{sec:preliminaries} with a $42$-week baseline, $z=2$, and
$\epsilon=10^{-8}$. PageRank uses damping $0.85$ and $10$ power iterations.
Gini coefficients are computed over active nodes in the predicted graph.

\subsection{Scenario instantiation}

\begin{center}\small
\begin{tabular}{@{}llll@{}}
\toprule
ID & Scenario               & Target                 & Shock \\
\midrule
S1 & Single protocol fail   & Highest-weight node    & 100\% \\
S2 & Bridge cluster fail    & All bridge nodes       & 100\% \\
S3 & Stablecoin de-peg      & All stablecoin nodes   & 50\%  \\
S4 & Sector lending shock   & All lending nodes      & 30\%  \\
S5 & Correlated stress      & Top-10 by weight       & 20\%  \\
\bottomrule
\end{tabular}
\end{center}

Scenario targets use protocol-sector metadata from \corpusname{}. For each
scenario and horizon, \sysname{} reports the deterministic loss on
$\widehat{G}_{t+h}$ and the sampled $\mathrm{CVaR}_{0.5}$ defined in
Section~\ref{sec:preliminaries}.

\subsection{Gate instantiation and ticket scoring}

The data-health gate uses the four checks in Section~\ref{sec:preliminaries}
with $\tau_{\mathrm{data}}=0.7$. Safe mode still releases monitor alerts and
scenario summaries, but suppresses intervention-level tickets
(\textsc{RecommendReduce} and \textsc{Contingency}). The confidence gate uses
$\tau_{\mathrm{conf}}=0.6$ and clamps each Monte Carlo coefficient of
variation to $[0,1]$ before computing alert confidence.

Feasible tickets are ranked by
\begin{equation}
\mathrm{Score}_t(u)
=
w_u\cdot \bar{C}_t\cdot \mathrm{Imp}_t,
\end{equation}
where $w_u\in\{0.25,0.50,0.75,1.00\}$ is the playbook severity weight for
the four ordered actions and $\mathrm{Imp}_t$ is the mean scenario CVaR
(default $1.0$ when no scenario summary is available).

\subsection{End-to-end procedure}

\begin{algorithm}[h]
\caption{\sysname{}: one decision epoch.}
\label{alg:agent_loop}
\small
\begin{algorithmic}[1]
\Require $(G_t,X_t)$; horizons $\mathcal{H}$; scenarios
$\mathcal{S}_0$; thresholds
$(\tau_{\mathrm{data}},\tau_{\mathrm{conf}},z,\pi_{\min})$; MC count $M$
\Ensure Alerts $\mathcal{A}_t$; scenario summary $\mathcal{R}_t$;
tickets $\mathcal{D}_t$
\State $\operatorname{DH}_t\gets\mathrm{DataHealth}(G_t,X_t)$
\State $\mathrm{SAFE\_MODE}_t\gets
       \mathbb{I}\{\operatorname{DH}_t<\tau_{\mathrm{data}}\}$
\ForAll{$h\in\mathcal{H}$}
  \State $P_{t,h}\gets\text{\fmname.Forecast}(G_t,X_t,h)$
  \State $\widehat{G}_{t+h}\gets
         \mathrm{BuildPredGraph}(P_{t,h};\pi_{\min})$
  \State $\{\widetilde{G}^{(m)}_{t+h}\}_{m=1}^M\gets
         \mathrm{MCSample}(P_{t,h})$
  \State Compute monitor statistics on $\widehat{G}_{t+h}$, attach rolling
         baselines, and derive alerts $\mathcal{A}_{t,h}$
  \State Compute alert confidences $C_t(\cdot)$ from sampled monitor
         dispersion
  \ForAll{$s\in\mathcal{S}_0$}
    \State Compute deterministic loss $L(s;\widehat{G}_{t+h})$ and sampled
           $\mathrm{CVaR}_{0.5}(s,h)$
  \EndFor
\EndFor
\State $\mathcal{D}_t\gets
       \mathrm{PlaybookDecision}(\mathcal{A}_t,\mathcal{R}_t,
       \operatorname{DH}_t,\mathrm{SAFE\_MODE}_t,\tau_{\mathrm{conf}})$
\State \Return $(\mathcal{A}_t,\mathcal{R}_t,\mathcal{D}_t)$
\end{algorithmic}
\end{algorithm}
