\section{Reference Methods}
\label{app:reference-methods}

\begin{center}\small
\begin{tabularx}{\linewidth}{@{}lllX@{}}
\toprule
ID                              & Predictor      & Policy                & Role \\
\midrule
\texttt{h1\_weighted\_degree}   & ---            & heuristic alert       & Streaming anomaly baseline (\texttt{b2}) \\
\texttt{m1\_persistence\_rules} & $G_{t+h}\!=\!G_t$ & rule engine        & Decision baseline \\
\texttt{m2\_snapshot\_llm}      & current snap   & LLM                   & LLM-only ablation (no forecast) \\
\texttt{m3\_evolvegcn}          & EvolveGCN      & ---                   & Learned-GNN baseline \\
\texttt{m4\_fm\_only}           & \fmname{}      & ---                   & FM-only ablation \\
\texttt{m5\_fm\_rules}          & \fmname{}      & rule engine           & FM + rules \\
\texttt{m6\_fm\_llm}            & \fmname{}      & LLM                   & Full FM + LLM stack \\
\texttt{m7\_fm\_llm\_gated}     & \fmname{}      & LLM + safety gate     & Safety-gated FM + LLM \\
\bottomrule
\end{tabularx}
\end{center}

The eight methods expose all four cuts of the four-layer ablation:
adding the predictor layer
(\texttt{m1}$\!\to\!$\texttt{m5}), swapping the decision layer
(\texttt{m5}$\!\to\!$\texttt{m6}), adding the safety gate
(\texttt{m6}$\!\to\!$\texttt{m7}), and removing the predictor from
the LLM stack (\texttt{m2}$\!\leftrightarrow\!$\texttt{m6}). All
methods conform to a shared
\texttt{predict\_graph}\,/\,\texttt{decide\_actions} interface;
adding a ninth method is a single-file change.

\paragraph{LLM model panel and decoding.}
All LLM-bearing methods (\texttt{m2}, \texttt{m6}, \texttt{m7}) are
evaluated under three decision-layer configurations:
Claude~Opus~4.7 (main), Claude~Sonnet~4.6 (within-family,
tier-below ablation), and Google~Gemini~2.5~Pro (cross-family
ablation). Each runs at temperature $0$ and $\max\_tokens=4096$;
self-consistency is probed with three repeated calls per week and
Jaccard overlap on emitted ticket targets and severities.

The LLM-as-judge for the explanation-quality axis is a
three-model panel chosen so the judge tier is at or above the
decision tier on the public 2026 Artificial Analysis index:
Claude~Opus~4.8 (within-family upgrade, strictly above Opus~4.7),
Google~Gemini~2.5~Pro, and OpenAI~GPT-5.5 (cross-family
upgrades). The Gemini and GPT judges are reasoning-by-default
models; we attach OpenRouter's $\mathrm{reasoning}=
\{\mathrm{effort:minimal}\}$ control to both so the judge
thinking budget matches the non-reasoning Anthropic baseline.
Claude~Haiku~4.5 from a pilot run is reported as a weak-judge
reference. Every model is served through the OpenRouter unified
API; observed cost is on the order of a few US dollars per
full sweep of the 29-week test split.
