\section{Statistical Significance and Matched-Budget Analysis}
\label{app:stats}

All headline metrics are means over the $n\!=\!29$ scored test
weeks. This appendix reports week-level uncertainty for the central
comparisons: 95\% percentile bootstrap confidence intervals
($10{,}000$ resamples of weeks with replacement; F1 is recomputed
from the resampled mean precision and recall) and two-sided paired
sign-flip permutation tests ($20{,}000$ permutations, methods
aligned by week). Analysis code is released with the harness
(\texttt{scripts/bootstrap\_stats.py},
\texttt{scripts/matched\_budget.py}).

\subsection{Confidence intervals}
\label{app:stats-ci}

\begin{table}[!htbp]
\centering
\footnotesize
\setlength{\tabcolsep}{5pt}
\caption{95\% bootstrap CIs for the decision-quality headline
numbers (decision LLM in parentheses; judge is Claude~Opus~4.8
throughout). \textsuperscript{\ddag}\texttt{m1}'s per-week
distribution comes from a local re-run of the released harness:
its aggregate F1 ($0.0081$) brackets the published GPU-run value
($0.0076$), and the recall@$k$ and stressed-pool size reproduce
exactly, but with ${<}1$ ticket per week a few borderline tickets
flip across environments (re-run precision $0.633$ vs published
$0.720$), so the \texttt{m1} interval should be read as
order-of-magnitude.}
\label{tab:stats_ci}
\begin{tabular}{@{}lccc@{}}
\toprule
Configuration & F1 [95\% CI] & FIR [95\% CI] & Judge [95\% CI] \\
\midrule
\texttt{m1} rules\textsuperscript{\ddag} & 0.0081 [0.0041, 0.0123] & 0.000 & --- \\
\texttt{m2} (Opus~4.7)       & 0.0184 [0.0142, 0.0223] & 0.000 & 2.24 [2.10, 2.41] \\
\texttt{m6} (Opus~4.7)       & 0.0241 [0.0201, 0.0281] & 0.448 [0.293, 0.601] & 2.41 [2.21, 2.62] \\
\texttt{m7} (Opus~4.7)       & 0.0234 [0.0194, 0.0271] & 0.437 [0.282, 0.592] & 2.45 [2.24, 2.66] \\
\texttt{m6} (Sonnet~4.6)     & 0.0276 [0.0225, 0.0324] & 0.000 & 2.52 [2.28, 2.79] \\
\texttt{m7} (Sonnet~4.6)     & 0.0288 [0.0236, 0.0335] & 0.000 & 2.66 [2.41, 2.90] \\
\texttt{m6} (Gemini~2.5~Pro) & 0.0129 [0.0103, 0.0155] & 0.000 & 2.21 \\
\texttt{m7} (Gemini~2.5~Pro) & 0.0139 [0.0111, 0.0167] & 0.000 & 2.38 \\
\bottomrule
\end{tabular}
\end{table}

\subsection{Paired permutation tests}
\label{app:stats-perm}

\begin{table}[!htbp]
\centering
\footnotesize
\setlength{\tabcolsep}{5pt}
\caption{Two-sided paired permutation $p$-values for the key
comparisons. Significant effects ($p<0.05$) in \textbf{bold}.}
\label{tab:stats_perm}
\begin{tabular}{@{}llr@{}}
\toprule
Comparison & Metric & $p$ \\
\midrule
\texttt{m6} vs \texttt{m2} (FM signal)        & F1   & \textbf{0.0002} \\
\texttt{m7} vs \texttt{m1} (full stack)       & F1   & \textbf{$<$0.0001} \\
\texttt{m7} vs \texttt{m6} (gate)             & F1   & 0.41 \\
\texttt{m7}$\times$Sonnet vs \texttt{m7}$\times$Opus & F1 & \textbf{0.0004} \\
\texttt{m6} vs \texttt{m2}                    & FIR  & \textbf{$<$0.0001} \\
\texttt{m6} vs \texttt{m2} (Opus~4.8 judge)   & Judge & 0.23 \\
\texttt{m6} vs \texttt{m2} (GPT-5.5 judge)    & Judge & \textbf{0.0002} \\
\texttt{m6} vs \texttt{m2} (Gemini judge)     & Judge & 0.77 \\
\texttt{m7} vs \texttt{m6} (Opus~4.8 judge)   & Judge & 1.00 \\
\texttt{m7}$\times$Sonnet vs \texttt{m7}$\times$Opus & Judge & 0.21 \\
\bottomrule
\end{tabular}
\end{table}

Three readings follow. (i)~The load-bearing quantitative claims---the
FM signal's F1 lift, the full stack's F1 lift over rules, the
Sonnet~4.6 F1 improvement, and the over-intervention cost---are
significant at $p\!<\!0.001$. (ii)~The explanation-quality lift of
the FM-grounded variants is judge-dependent: significant under
GPT-5.5, positive but not significant under Opus~4.8 ($p\!=\!0.23$),
and absent under the (noisiest) Gemini judge. We therefore read the
judge axis as directional evidence rather than a confirmed effect.
(iii)~The safety gate's effects on F1 and judge score are
indistinguishable from noise on clean data, consistent with its
characterisation as a reserve mechanism (\S\ref{sec:lessons}).

\subsection{Matched-budget recall@$k$}
\label{app:stats-budget}

Methods emit different numbers of ticket targets per week
(\texttt{m1} $2.1$, \texttt{m2} $4.9$, \texttt{m7} $6.3$,
\texttt{m6} $6.5$, \texttt{m7}$\times$Sonnet $7.6$), and unbudgeted
recall mechanically favours methods that flag more protocols. To separate
target \emph{quality} from target \emph{volume}, we truncate every
method to its top-$k$ targets per week (LLM variants ranked by their
own emitted risk score; \texttt{m1} by ticket confidence) and score
against the same stressed pool.

\begin{table}[!htbp]
\centering
\footnotesize
\setlength{\tabcolsep}{4pt}
\caption{Matched-budget recall@$k$ ($\times 10^{3}$) and
precision@$k$ on the 2025 test split. At matched budgets every LLM
variant beats the rules baseline ($p\!\leq\!0.0055$ vs \texttt{m1}
at all $k$), while the FM-grounded and raw-snapshot LLM variants
are statistically indistinguishable from each other (all pairwise
$p\!\geq\!0.10$) and the top-$k$ hit patterns of the three FM-fed
decision LLMs nearly coincide. \texttt{m1} row from the local
re-run (Table~\ref{tab:stats_ci} note).}
\label{tab:matched_budget}
\begin{tabular}{@{}lcccccc@{}}
\toprule
& \multicolumn{2}{c}{$k\!=\!1$} & \multicolumn{2}{c}{$k\!=\!2$} & \multicolumn{2}{c}{$k\!=\!3$} \\
\cmidrule(lr){2-3}\cmidrule(lr){4-5}\cmidrule(lr){6-7}
Method & R@1 & P@1 & R@2 & P@2 & R@3 & P@3 \\
\midrule
\texttt{m1} rules            & 0.71 & 0.24 & 1.71 & 0.28 & 2.45 & 0.26 \\
\texttt{m2} (Opus~4.7)       & 1.53 & 0.52 & 3.47 & 0.55 & 5.70 & 0.59 \\
\texttt{m6} (Opus~4.7)       & 1.64 & 0.55 & 3.29 & 0.53 & 5.30 & 0.56 \\
\texttt{m7} (Opus~4.7)       & 1.64 & 0.55 & 3.47 & 0.55 & 5.30 & 0.56 \\
\texttt{m7} (Sonnet~4.6)     & 1.64 & 0.55 & 3.47 & 0.55 & 5.30 & 0.56 \\
\bottomrule
\end{tabular}
\end{table}

The matched-budget view decomposes the headline F1 result into two
distinct effects. Against the \emph{rules baseline}, LLM targeting
is genuinely better per target: at every $k$, precision@$k$ roughly
doubles ($0.52$--$0.59$ vs $0.24$--$0.28$) and recall@$k$ is
significantly higher ($p\!\leq\!0.0055$). Against the
\emph{raw-snapshot LLM}, however, the FM's contribution is not a
higher per-target hit rate at the top of the ranking---at matched
$k$ the FM-fed and raw-snapshot variants are statistically
indistinguishable, and the FM-fed variants' top-$k$ targets are
nearly identical across decision LLMs because the evidence bundle
pins the highest-exposure protocols. The FM's F1 gain comes from
supporting a \emph{larger} target set at undiminished precision
(Table~\ref{tab:headline}), which is also where the
over-intervention risk concentrates: under Opus~4.7 the expanded
tail is escalated to intervention-level severity
($\mathrm{FIR}\!=\!0.448$), while Sonnet~4.6 expands the same set
without escalating it ($\mathrm{FIR}\!=\!0$).
