\section*{Limitations}
\label{sec:limitations}

\paragraph{Historical replay evaluation.}
We evaluate \sysname{} by replaying $283$ frozen weekly snapshots
of \corpusname{} (2020--2025), which lets us compare methods under
identical evidence and audit calibration, lead time, and ticket
quality. This setup does not measure production-integration factors
such as live data-feed reliability, operator workload, or threshold
retuning under changing supervisory priorities. These factors affect
deployment policy rather than the central comparison studied here:
whether structured forecast evidence improves auditable
human-in-the-loop risk monitoring.

\paragraph{Single domain.}
\benchname{} evaluates a single on-chain risk surface (DeFi
inter-protocol credit exposure). Generalisation to NFT lending,
perpetual derivatives, or cross-chain bridge networks is untested
and will require domain-specific re-calibration of the conformal
split and the stressed-set percentile $\pi$.

\paragraph{Weekly resolution.}
The pipeline operates at weekly granularity, but several DeFi shocks
unfold within hours---Terra/Luna erased \$40B in under 48~hours. A
sub-hourly production deployment would require denser snapshot
ingestion and re-evaluation of conformal calibration on the
resulting denser time series. The $4$--$5$ week lead times we
report should be read as ``how early the weekly monitor turns'',
not as end-to-end alert latency.

\paragraph{Judge thinking-budget is held minimal.}
The cross-family judge panel (Claude~Opus~4.8, Google
Gemini~2.5~Pro, OpenAI~GPT-5.5) is run with reasoning effort set
to \emph{minimal} so the comparison against the
non-reasoning Anthropic baseline is a like-for-like comparison of
intrinsic model capability rather than thinking budget. Default
reasoning mode on Gemini~2.5~Pro and GPT-5.5 would change the
reported scores; we treat the reasoning-on configuration as a
distinct evaluation surface and leave it for a follow-up study.
Practitioners deploying the judge at default reasoning settings
should re-calibrate the score thresholds reported here. Human-judge
calibration with practising supervisors remains the most pressing
methodological extension.

\paragraph{Decision-outcome proxy.}
\texttt{b5\_decision} scores tickets against a regulator-aligned
absolute-loss ground truth, which captures supervisory targeting
priority but not the counterfactual effect of supervisory
action---whether the recommended risk reduction would have changed
the subsequent contagion path. We therefore interpret decision
scores as evidence of targeting and explanation quality, not as a
causal estimate of intervention impact.
