\section{Empirical Evaluations}
\label{sec:evaluation}

We evaluate DeXposure-FM on the DeXposure dataset, focusing on three tasks: (i) \textit{multi-step forecasting} of edge-level exposures and network-level statistics, (ii) \textit{shock analysis} during major stress events (Terra/Luna, FTX), and (iii) \textit{imputation} of missing edges.

\subsection{Dataset and Experimental Setup}
\label{subsec:dataset}

\paragraph{Data source.}
We use the DeXposure dataset constructed from DeFiLlama API data, spanning March 2020 to August 2025 (283 weekly snapshots). Each snapshot contains protocol nodes with TVL measurements and directed edges representing credit exposures between protocols.

\paragraph{Data statistics.}
Table~\ref{tab:data-stats} summarizes the dataset characteristics. The network exhibits high edge persistence (mean overlap ratio 98.5\%), reflecting the stable nature of DeFi protocol interconnections.

\begin{table}[t]
\centering
\small
\begin{tabular}{lr}
\hline
\textbf{Statistic} & \textbf{Value} \\
\hline
Total snapshots & 283 weeks \\
Time range & 2020-03-23 $\sim$ 2025-08-18 \\
Mean nodes per week & 5,676 \\
Mean edges per week & 30,424 \\
Mean edge overlap ratio & 98.5\% \\
Protocol categories & $\sim$15 classes \\
\hline
\end{tabular}
\caption{DeXposure dataset statistics.}
\label{tab:data-stats}
\end{table}

\paragraph{Temporal split.}
We use a two-stage evaluation protocol:

\textit{Stage 1: Model selection via walk-forward cross-validation.}
We apply expanding window walk-forward cross-validation on pre-2025 data with 16 folds. Each fold uses a minimum of 104 training weeks, 12 validation weeks (for early stopping), and 8 test weeks. The window advances by 8 weeks per fold, accumulating more training data. This stage is used for hyperparameter selection and model comparison.

\textit{Stage 2: Hold-out evaluation.}
Final performance is reported on a strict 2025 hold-out set, which is never seen during training or validation:
\begin{itemize}
  \item \textbf{Training:} 2020-03-23 $\sim$ 2024-10-07 (238 weeks)
  \item \textbf{Validation:} 2024-10-14 $\sim$ 2024-12-30 (12 weeks, for early stopping)
  \item \textbf{Test:} 2025-01-06 $\sim$ 2025-08-18 (33 weeks, strict hold-out)
\end{itemize}
All results in this paper are from Stage 2 hold-out evaluation.

\paragraph{Forecast horizons vs. CV windows.}
The 8-week CV window controls how the temporal folds slide; within each window, the model predicts at multiple forecast horizons $h \in \{1, 3, 7, 14\}$ weeks ahead. These are orthogonal: the CV window determines sample collection, while $h$ determines how far into the future each prediction extends.

\paragraph{Models compared.}
We compare three approaches:
\begin{enumerate}
  \item \textbf{GraphPFN-Frozen:} Pre-trained GraphPFN encoder with frozen weights; only task-specific prediction heads are trained (linear probe).
  \item \textbf{DeXposure-FM:} Pre-trained GraphPFN encoder with end-to-end fine-tuning using differential learning rates.
\item \textbf{ROLAND:} Representative temporal GNN baseline with a GCN encoder and GRU temporal updates, trained from scratch.
\end{enumerate}

\subsection{Task I: Multi-step Forecasting}
\label{subsec:forecast}

\paragraph{Targets.}
We evaluate forecasts at horizons $h \in \{1, 3, 7, 14\}$ weeks for:
\begin{enumerate}
  \item \textbf{Edge existence:} Binary prediction of whether edge $(p,q)$ exists at $t+h$.
  \item \textbf{Edge weight:} Regression on log-scaled edge weight for existing edges.
  \item \textbf{Node TVL change:} Regression on $\Delta_{p,t+h} = \log(1+\text{TVL}_{t+h}) - \log(1+\text{TVL}_t)$.
\end{enumerate}

\paragraph{Metrics.}
For edge existence, we report AUPRC (area under precision-recall curve) and AUROC. For edge weight and node predictions, we report MAE and RMSE on log-scaled values.

\paragraph{Results.}
Table~\ref{tab:main-results} presents the main forecasting results on the 2025 hold-out test set (partial; remaining entries \textit{TBD}).

\begin{table}[t]
\centering
\small
\setlength{\tabcolsep}{4pt}
\begin{tabular}{llcccccc}
\hline
& & \multicolumn{2}{c}{\textbf{Edge Exist}} & \multicolumn{2}{c}{\textbf{Edge Weight}} & \multicolumn{2}{c}{\textbf{Node $\Delta$TVL}} \\
\textbf{Model} & $h$ & AUROC & AUPRC & MAE & RMSE & MAE & RMSE \\
\hline
\multirow{4}{*}{DeXposure-FM}
& 1 & \textbf{0.994} & \textbf{0.967} & \textbf{2.540} & \textbf{3.420} & \textbf{0.058} & \textbf{0.400} \\
& 3 & \textbf{0.994} & \textbf{0.966} & \textbf{2.540} & \textbf{3.480} & \textbf{0.115} & \textbf{0.605} \\
& 7 & \textbf{0.994} & \textbf{0.967} & \textbf{2.550} & \textbf{3.490} & \textbf{0.197} & \textbf{0.840} \\
& 14 & \textit{TBD} & \textit{TBD} & \textit{TBD} & \textit{TBD} & \textit{TBD} & \textit{TBD} \\
\hline
\multirow{4}{*}{GraphPFN-Frozen}
& 1 & 0.988 & 0.937 & 3.250 & 4.260 & \textbf{0.058} & 0.401 \\
& 3 & 0.987 & 0.934 & 3.250 & 4.290 & 0.118 & 0.606 \\
& 7 & 0.987 & 0.936 & 3.210 & 4.250 & 0.196 & 0.845 \\
& 14 & 0.985 & 0.931 & 3.190 & 4.320 & 0.298 & 1.132 \\
\hline
\multirow{4}{*}{ROLAND}
& 1 & 0.957 & 0.852 & 3.356 & 4.305 & 0.061 & 0.403 \\
& 3 & 0.955 & 0.853 & 3.394 & 4.301 & 0.121 & 0.607 \\
& 7 & 0.883 & 0.750 & 3.489 & 4.841 & 0.210 & 0.844 \\
& 14 & 0.955 & 0.850 & 3.299 & 4.178 & 0.303 & 1.133 \\
\hline
\end{tabular}
\caption{Multi-step forecasting results on 2025 hold-out test set. DeXposure-FM = Fine-tuned, GraphPFN-Frozen = Frozen (linear probe). \textit{TBD} indicates runs not completed yet.}
\label{tab:main-results}
\end{table}

\paragraph{Key findings.}
\begin{enumerate}
  \item \textbf{Edge existence:} DeXposure-FM achieves consistently high performance across horizons with AUROC 0.994 and AUPRC 0.966--0.967, outperforming GraphPFN-Frozen (0.985--0.988/0.931--0.937) and ROLAND (0.883--0.957/0.750--0.853).
  \item \textbf{Edge weight:} DeXposure-FM shows substantial and stable improvement in weight prediction with MAE 2.540--2.550 across h=1/3/7, vs.\ 3.190--3.250 (Frozen) and 3.299--3.489 (ROLAND), a 22\% reduction.
  \item \textbf{Node prediction:} Node TVL change prediction degrades with horizon as expected: DeXposure-FM MAE increases from 0.058 (h=1) to 0.197 (h=7), comparable to Frozen (0.058--0.196) and below ROLAND at longer horizons (0.210 at h=7; 0.303 at h=14).
  \item \textbf{Horizon stability:} DeXposure-FM maintains stable edge prediction across horizons while Frozen shows slight degradation; ROLAND drops at h=7 (AUROC 0.883, AUPRC 0.750) and recovers at h=14 (0.955/0.850).
\end{enumerate}

\subsection{Task II: Financial Stability Analysis}
\label{subsec:stability}

We conduct comprehensive financial stability analysis, combining systemic risk measurement, historical shock analysis, and contagion simulation. This task directly addresses macro-prudential policy applications.

\subsubsection{Systemic Risk Measurement}
\label{subsubsec:systemic-risk}

We compute protocol-level and network-level risk indicators for each weekly snapshot.

\paragraph{Protocol-level systemic importance score (SIS).}
For each protocol $p$, we define:
\begin{equation}
\text{SIS}_p = \alpha \cdot \text{PageRank}_p + \beta \cdot \text{TailExposure}_p + \gamma \cdot \log(\text{TVL}_p),
\label{eq:sis}
\end{equation}
where $\text{TailExposure}_p$ measures the concentration of $p$'s largest exposures (ratio of top-5 exposures to total), and $\alpha, \beta, \gamma$ are normalized weights summing to 1.

\paragraph{Sector spillover index.}
We aggregate exposures into a sector-to-sector matrix $\mathbf{S} \in \mathbb{R}^{K \times K}$, where $S_{ij}$ is the total exposure from sector $i$ to sector $j$. The spillover index is the HHI of off-diagonal elements:
\begin{equation}
\text{SpilloverIndex} = \text{HHI}\left(\{S_{ij} : i \neq j\}\right).
\end{equation}

\paragraph{Early-warning indicators.}
We track structural change rates that may signal emerging instability:
\begin{itemize}
  \item Density change: $\Delta\rho_t = (\rho_t - \rho_{t-1})/\rho_{t-1}$
  \item Concentration spike: $\Delta\text{HHI}_t > 2\sigma$ (two standard deviations above mean)
  \item Assortativity shift: rapid changes in degree correlation
\end{itemize}

\subsubsection{Shock Event Analysis}
\label{subsubsec:shock-events}

We analyze model behavior during two major DeFi stress events.

\paragraph{Events analyzed.}
\begin{enumerate}
  \item \textbf{Terra/Luna collapse} (May 9, 2022): The UST algorithmic stablecoin lost its dollar peg, triggering cascading liquidations. Analysis window: April 25 -- May 23, 2022.
  \item \textbf{FTX collapse} (November 7, 2022): The FTX exchange failure and resulting contagion through FTT token exposures. Analysis window: October 31 -- November 21, 2022.
\end{enumerate}

\paragraph{Analysis framework.}
For each event, we examine a pre/event/post window and report both structural shifts and forecasting quality on economically material edges:
\begin{enumerate}
  \item \textbf{Network structure changes:} TVL, edge count, Gini coefficient, HHI.
  \item \textbf{Forecasting quality under stress:} AUPRC, Recall@K, and TVL-weighted MAE reported for pre/event/post windows, with $\Delta(\text{event} - \text{pre})$.
  \item \textbf{Early warning signals:} whether structural indicators spiked before the event.
\end{enumerate}

\paragraph{Results.}
Table~\ref{tab:shock-results} shows network structure changes during the two stress events.

\begin{table}[t]
\centering
\small
\begin{tabular}{lcccc}
\hline
\textbf{Event} & \textbf{Pre-TVL (\$B)} & \textbf{Post-TVL (\$B)} & \textbf{$\Delta$TVL} & \textbf{$\Delta$Edges} \\
\hline
Terra/Luna & 257.1 & 171.0 & $-$33.5\% & +9.4\% \\
FTX & 127.0 & 177.2 & +39.5\% & $-$3.3\% \\
\hline
\end{tabular}
\caption{Network structure changes during stress events. Terra/Luna shows classic flight-to-quality pattern with TVL collapse but edge count increase as capital reorganizes. FTX shows TVL rebound as users withdraw from centralized venues.}
\label{tab:shock-results}
\end{table}

\subsubsection{Contagion Simulation}
\label{subsubsec:contagion}

We implement a DebtRank-style contagion simulation to assess systemic loss propagation.

\paragraph{Shock propagation mechanism.}
Given an initial shock to protocol $p_0$ with loss ratio $\delta_0$:
\begin{enumerate}
  \item \textbf{Initialize:} $\text{Loss}_{p_0} = \delta_0 \cdot \text{TVL}_{p_0}$
  \item \textbf{Propagate:} For each creditor $q$ with exposure $E_{qp_0}$ to $p_0$:
  \begin{equation}
    \text{Loss}_q^{(1)} = E_{qp_0} \cdot \delta_0
  \end{equation}
  \item \textbf{Iterate:} If $\text{Loss}_q^{(r)} > \tau \cdot \text{TVL}_q$, protocol $q$ becomes distressed and propagates losses to its creditors.
  \item \textbf{Terminate:} When no new protocols become distressed.
\end{enumerate}

\paragraph{Simulation scenarios.}
We simulate counterfactual shocks using actual network structure:
\begin{itemize}
  \item \textbf{Stablecoin de-peg:} 50\% TVL loss to major stablecoins (USDC, DAI)
  \item \textbf{Exchange failure:} Complete TVL loss to centralized exchange protocols
  \item \textbf{Bridge exploit:} 100\% loss to cross-chain bridge protocols
\end{itemize}

\paragraph{Metrics.}
\begin{itemize}
  \item \textbf{Total system loss:} $\sum_p \text{Loss}_p$ after convergence
  \item \textbf{Contagion depth:} Number of propagation rounds before convergence
  \item \textbf{Affected protocols:} Count of protocols with $\text{Loss} > 0$
\end{itemize}

Table~\ref{tab:contagion-results} presents contagion simulation results on the May 2022 network snapshot (4,329 nodes, 17,721 edges).

\begin{table}[t]
\centering
\small
\begin{tabular}{lccc}
\hline
\textbf{Scenario} & \textbf{System Loss (\%)} & \textbf{Depth} & \textbf{Affected} \\
\hline
Single protocol (50\% shock) & 0.00 & 0 & 0 \\
Multi-protocol (top 5) & 0.00 & 0 & 0 \\
Stablecoin cluster & 1.10 & 1 & 153 \\
Bridge exploit (100\% loss) & \textbf{5.27} & 1 & 90 \\
\hline
\end{tabular}
\caption{Contagion simulation results. Bridge protocols emerge as the primary systemic risk vector---despite shocking only 22 nodes, they cause the largest system-wide loss (5.27\% TVL). Single-protocol failures show minimal contagion, indicating network resilience to isolated shocks.}
\label{tab:contagion-results}
\end{table}

\subsection{Task III: Imputation}
\label{subsec:imputation}

We evaluate the model's ability to reconstruct missing edges, simulating incomplete network observations that are common in real-world DeFi data collection.

\paragraph{Masking protocol.}
We apply Missing Completely at Random (MCAR) masking at three severity levels:
\begin{itemize}
  \item \textbf{Light (10\%):} Simulates minor data collection gaps
  \item \textbf{Moderate (20\%):} Tests reconstruction under typical incompleteness
  \item \textbf{Heavy (30\%):} Stress-tests model capacity with significant missing data
\end{itemize}

\paragraph{Masking types.}
\begin{enumerate}
  \item \textbf{Edge masking:} Randomly remove edges from the observed graph
  \item \textbf{Node masking:} Mask node attributes (TVL) and require reconstruction
  \item \textbf{Combined masking:} Simultaneously mask both edges and node attributes
\end{enumerate}

\paragraph{Metrics.}
For masked edges, we report:
\begin{itemize}
  \item AUPRC for edge existence reconstruction (can the model recover which edges were masked?)
  \item MAE for edge weight reconstruction (how accurately can masked weights be imputed?)
\end{itemize}

\paragraph{Results.}
Table~\ref{tab:imputation-results} summarizes imputation performance using DeXposure-FM.

\begin{table}[t]
\centering
\small
\begin{tabular}{cccc}
\hline
\textbf{Mask Rate} & \textbf{Edge Recall} & \textbf{Weight MAE} & \textbf{Node MAE} \\
\hline
10\% & 0.985 & 2.54 & 0.067 \\
20\% & 0.985 & 2.54 & 0.068 \\
30\% & 0.984 & 2.54 & 0.070 \\
\hline
\end{tabular}
\caption{Imputation performance at different masking rates using DeXposure-FM. The model maintains $>$98\% edge recall even with 30\% edges masked, demonstrating robust reconstruction capability. Edge weight MAE matches forecasting performance ($\sim$2.54), confirming the model learns genuine exposure patterns rather than trivial baselines.}
\label{tab:imputation-results}
\end{table}

\subsection{Discussion}
\label{subsec:discussion}

\paragraph{High edge overlap enables strong baselines.}
The 98.5\% mean edge overlap in DeFi networks means that predicting ``all edges persist'' achieves high accuracy. This makes absolute AUPRC/AUROC less informative than relative improvements. DeXposure-FM's 3\% AUPRC gain over GraphPFN-Frozen (0.967 vs.\ 0.937) represents meaningful improvement in identifying the 1.5\% of edges that do change.

\paragraph{Weight prediction benefits most from fine-tuning.}
The 22\% MAE reduction in edge weight prediction (2.54 vs.\ 3.25) demonstrates that fine-tuning captures domain-specific exposure dynamics that frozen encoders miss. This is critical for policy applications where exposure magnitudes determine systemic risk.

\paragraph{Imputation recall reflects network stability.}
The 98\%+ edge recall in imputation experiments directly reflects the underlying 98.5\% edge overlap in DeFi networks---the model learns that edges typically persist, which is the correct inductive bias for this domain. Crucially, this is not a trivial baseline: the model must also predict accurate edge \textit{weights} (MAE $\sim$2.54, matching forecasting performance), and the recall remains stable even at 30\% masking where a naive ``all edges exist'' heuristic would fail on masked edges. This robustness enables practical applications: (i) reconstructing incomplete network observations from partial API data, (ii) validating data collection pipelines by cross-checking imputed vs.\ observed edges, and (iii) generating synthetic stress scenarios by selectively masking high-importance edges.

\paragraph{Bridge protocols as systemic risk vectors.}
Contagion simulations identify cross-chain bridges as disproportionate risk concentrators---shocking 22 bridge nodes causes 5.27\% system-wide loss, exceeding stablecoin scenarios (79 nodes, 1.10\% loss). This aligns with historical bridge exploits (Ronin, Wormhole) and suggests regulatory attention to bridge capitalization.

\paragraph{Limitations.}
DeXposure-FM h=14 results are pending due to computational constraints. The contagion model assumes linear loss propagation and does not capture feedback effects (e.g., liquidation cascades). Node TVL predictions degrade at longer horizons (MAE 0.058 at h=1 vs.\ 0.197 at h=7), reflecting inherent uncertainty in protocol-level forecasts.
